Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-08-07 tex/ms.tex
add lee 2011 (xray analysis) to ref list
better wording

XXX Alternative 2 XXX.
Because the residual column vector $\Delta$ of equation
\ref{eq:spectroscopicLF} is additive with respect to the mean model
$\mu$, sharp spectral features in the mean model (such as absorption
lines) can be artificially diluted or enhanced, affecting the inferred
physical parameters. To mitigate this we construct a noise model where the
residual column vector is taken to be additive in the log and is
therefore multiplicative with respect to the mean model $\mu$.  That
is,
\begin{eqnarray}\label{eq:spectroscopicLFalt2} 
\Delta &\equiv&
\ln d - \ln \mu(\theta) - f(\alpha) \\
\sigma_{n} & = & \sigma'_n / d
\quad ,
\end{eqnarray}
where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before, and
$\sigma'_{n}$ are now the observational uncertainties. In this
formulation the the mean model $\mu$ will be effectively multiplied by
$e ^{f(\alpha)}$ which, given our quadratic form for $f(\alpha)$, is
equivalent to a large scale Gaussian ({\color{red} could we just add
this to the covariance matrix with a single long quadratic ?}).  This
logarithmic formulation requires that $d$ be everywhere positive, and
the uncertainties will be truncated to only allow positive values and
incorrect in detail.  However, at high signal to noise they should be
approximately correct. {\color{red} As I understand it, additional
`bad lines' in the mean model could be accounted for using narrow
quadratics in the covariance matrix, though their interpretation would
be hellish.}

@@

>>>>

XXX Alternative 2 XXX.
Because the residual column vector $\Delta$ of equation
\ref{eq:spectroscopicLF} is additive with respect to the mean model
$\mu$, sharp spectral features in the mean model (such as absorption
lines) can be artificially diluted or enhanced, affecting the inferred
physical parameters. To mitigate this we construct a noise model where the
residual column vector is taken to be additive in the log and is
therefore multiplicative with respect to the mean model $\mu$.  That
is,
\begin{eqnarray}\label{eq:spectroscopicLFalt2} 
\Delta &\equiv&
\ln d - \ln \mu(\theta) - f(\alpha) \\
\sigma_{n} & = & \sigma'_n / d
\quad ,
\end{eqnarray}
where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before, and
$\sigma'_{n}$ are now the observational uncertainties. In this
formulation the the mean model $\mu$ will be effectively multiplied by
$e ^{f(\alpha)}$ ({\color{red} could we just add
this to the covariance matrix with a single long quadratic ?}).  This
logarithmic formulation requires that $d$ be everywhere positive, and
the uncertainties will be truncated to only allow positive values and
incorrect in detail.  However, at high signal to noise they should be
approximately correct. {\color{red} As I understand it, additional
`bad lines' in the mean model could be accounted for using narrow
quadratics in the covariance matrix, though their interpretation would
be hellish.}

@@

\bibitem[Lee et al.(2011)]{xray_calunc} Lee, H., Kashyap, V.~L., 
van Dyk, D.~A., et al.\ 2011, \apj, 731, 126
